**Preprinting Microbiology**

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add text re public comments speeding peer review
Close #24
Provide a citation to the first microbiology PP
Closes #18

The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication). In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.

***Conclusions.*** An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer review. A number of critical concerns remain about how widespread their adoption will be, how they will be perceived by traditional journals and other scientists, and whether traditional peer-review will adapt to the new scientific trends and technologies. Regardless, preprints should offer a great opportunity for both scientists and journals to publish high quality science.

>>>>

The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. As the mSphereDirect mechanism evolves and is perhaps adopted by other journals, it will be interesting to see whether public feedback will be used to futher streamline the editorial process. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication). In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.

***Conclusions.*** Since the first microbiology-affiliated preprint was posted on bioRxiv in November 2013 [@Hockett2013], an increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer review. A number of critical concerns remain about how widespread their adoption will be, how they will be perceived by traditional journals and other scientists, and whether traditional peer-review will adapt to the new scientific trends and technologies. Regardless, preprints should offer a great opportunity for both scientists and journals to publish high quality science.
